Constraint Programming Algorithms used in Gecode

### 2014-05-19 paper.tex
improved figure for branch-and-bound
moved figure
corrections Michael

		\node[rectangle,draw] at (-1, 1) (levelTwoElementOne) {$y = 1$};
		\coordinate[left=0.2cm of levelOne.south] (levelOnePointOne);
  		\path[arrow] (levelTwoElementOne) -- (levelOnePointOne);
		\node[rectangle,draw] at (-1, 0) (levelThreeElementOne) {\Checkmark};
  		\path[arrow] (levelThreeElementOne) -- (levelTwoElementOne);
		\node[rectangle,draw] at (1, 1) (levelTwoElementTwo) {$y = 2$};
		\coordinate[right=0.2cm of levelOne.south] (levelOnePointTwo);
  		\path[arrow] (levelTwoElementTwo) -- (levelOnePointTwo);
		\node[rectangle,draw] at (1, 0) (levelThreeElementTwo) {\Checkmark};
  		\path[arrow] (levelThreeElementTwo) -- (levelTwoElementTwo);
	\end{tikzpicture}
	\caption{search tree with constraint propagation}
	\label{fig:smallTree}
	\end{figure}

@@

	\begin{figure}
		\center
		\begin{tikzpicture}
			\coordinate (a) at (0, 0);
			\coordinate (b) at (4, 0);
			\coordinate (c) at (5, 3);
			\coordinate (d) at (3, 6);
			\coordinate (e) at (-1, 2);
			\coordinate (f) at (2, 0);
			\coordinate (g) at (intersection of e--c and f--d);

			\draw[very thick] (a) -- (b) -- (c) -- (d) -- (e) -- (a);
			\draw (a) -- (b) -- (c) -- (e) -- (a);
			\draw (f) -- (g) -- (c) -- (b) -- (f);
			\draw[fill=blue, fill opacity=0.2] (c) -- (d) -- (e) -- (c);
			\draw[fill=green, fill opacity=0.2] (a) -- (f) -- (g) -- (e) -- (a);
			\draw[fill=brown, fill opacity=0.2] (f) -- (g) -- (c) -- (b) -- (f);
			\node at (2.75, 3.75) {$P_0$};
			\node at (1.25, 1.25) {$P_1$};
			\node at (3.75, 1.75) {$P_2$};
		\end{tikzpicture}	
		\caption{Splitting of a search space into three subproblems and the possible candidates for solutions}
		\label{fig:branchAndBound}
	\end{figure}

	The basic concept for finding solutions in branch-and-bound is an enumeration of all possible candidates. Therefore, it is necessary to separate the search space in an appropriate way, which is the task for the branch-and-reduce step. This step is very similar to the concept of branching, it also depends on a certain heuristic to divide the search space into two or even more disjoint parts. This heuristic can either be selected by the user or be a general one, like splitting the biggest variable domain into two equal sized parts. If the basic search space contains a big amount of possible candidate solutions one reduction may not be enough and therefore this step is applied recursively to the newly create subproblems. This process can be stopped if the number of solutions is reduced to an amount, where it is possible to enumerate all of them and check if they are optimal. A possible division into subproblems can be seen in \reffig{fig:branchAndBound}, where for legibility branch-and-reduce was applied only twice: The first execution split the problem into $P_0$ and $P'_0$, which was then split again into $P_1$ and $P_2$.

@@

	\subsubsection{Limited Discrepancy Search}
	The limited discrepancy search falls into the category of best-first searches and was first mentioned by Harvey and Ginsberg \cite{limitedDiscrepancy}. It depends on branching heuristics for the tree, which are determined through branching strategies. The basic concept is that during a chronological backtrack search a wrong turn close to the root is first of all very expensive. Second, heuristics work worse the farther away from the solution they are applied. Therefore, decisions close to the root node are likely to fail. Consequently, in a depth-first search the worst decisions are the most expensive ones. The limited discrepancy search solves exactly this problem as it suggests to change rather the decisions made close to the root than the ones the search made later. The improvement compared to a chronological backtrack was shown by experimental results and theoretically proven in \cite{limitedDiscrepancy}.

>>>>

		\node[rectangle,draw] at (-1, 1) (levelTwoElementOne) {$y = 1$};
		\coordinate[left=0.2cm of levelOne.south] (levelOnePointOne);
  		\path[arrow] (levelTwoElementOne) -- (levelOnePointOne);
		\node[rectangle,draw] at (-1, 0) (levelThreeElementOne) {\Checkmark};
  		\path[arrow] (levelThreeElementOne) -- (levelTwoElementOne);
		\node[rectangle,draw] at (1, 1) (levelTwoElementTwo) {$y = 2$};
		\coordinate[right=0.2cm of levelOne.south] (levelOnePointTwo);
  		\path[arrow] (levelTwoElementTwo) -- (levelOnePointTwo);
		\node[rectangle,draw] at (1, 0) (levelThreeElementTwo) {\Checkmark};
  		\path[arrow] (levelThreeElementTwo) -- (levelTwoElementTwo);
	\end{tikzpicture}
	\caption{search tree with constraint propagation}
	\label{fig:smallTree}
	\end{figure}\begin{figure}
		\center
		\subfloat[First step]
		{
			\begin{tikzpicture}
				\coordinate (a) at (1, 0);
				\coordinate (b) at (3, 0);
				\coordinate (c) at (3.5, 2);
				\coordinate (d) at (2, 4);
				\coordinate (e) at (0.5, 1);
				\coordinate (f) at (2, 0);
				\coordinate (g) at (intersection of e--c and f--d);

				\draw[very thick] (a) -- (b) -- (c) -- (d) -- (e) -- (a);
				\draw (a) -- (b) -- (c) -- (e) -- (a);
				\draw[fill=blue, fill opacity=0.2] (c) -- (d) -- (e) -- (c);
				\draw[fill=green, fill opacity=0.2] (a) -- (b) -- (c) -- (e) -- (a);
				\node at (2.25, 2.75) {$P_0$};
				\node at (1.75, 0.75) {$P_0'$};
			\end{tikzpicture}	
		}
		\subfloat[Second step]
		{		
			\begin{tikzpicture}
				\coordinate (a) at (1, 0);
				\coordinate (b) at (3, 0);
				\coordinate (c) at (3.5, 2);
				\coordinate (d) at (2, 4);
				\coordinate (e) at (0.5, 1);
				\coordinate (f) at (2, 0);
				\coordinate (g) at (intersection of e--c and f--d);

				\draw[very thick] (a) -- (b) -- (c) -- (d) -- (e) -- (a);
				\draw (a) -- (b) -- (c) -- (e) -- (a);
				\draw (f) -- (g) -- (c) -- (b) -- (f);
				\draw[fill=blue, fill opacity=0.2] (c) -- (d) -- (e) -- (c);
				\draw[fill=green, fill opacity=0.2] (a) -- (f) -- (g) -- (e) -- (a);
				\draw[fill=brown, fill opacity=0.2] (f) -- (g) -- (c) -- (b) -- (f);
				\node at (2.25, 2.75) {$P_0$};
				\node at (1.25, 0.75) {$P_1$};
				\node at (2.75, 1.25) {$P_2$};
			\end{tikzpicture}	
		}
		\caption{Splitting of a search space into three subproblems and the possible candidates for solutions}
		\label{fig:branchAndBound}
	\end{figure}

@@

	The basic concept for finding solutions in branch-and-bound is an enumeration of all possible candidates. Therefore, it is necessary to separate the search space in an appropriate way, which is the task for the branch-and-reduce step. This step is very similar to the concept of branching, it also depends on a certain heuristic to divide the search space into two or even more disjoint parts. The heuristic can either be selected by the user or be a general one, like splitting the biggest variable domain into two equal sized parts. If the basic search space contains a big amount of possible candidate solutions one reduction may not be enough and therefore this step is applied recursively to the newly create subproblems. This process can be stopped if the number of solutions is reduced to an amount, where it is possible to enumerate all of them and check if they are optimal. A possible division into subproblems can be seen in \reffig{fig:branchAndBound}, where for legibility branch-and-reduce was applied only twice: The first execution split the problem into $P_0$ and $P'_0$, which was then split again into $P_1$ and $P_2$.

@@

	\subsubsection{Limited Discrepancy Search}
	The limited discrepancy search falls into the category of best-first searches and was first mentioned by Harvey and Ginsberg \cite{limitedDiscrepancy}. It depends on branching heuristics for the tree, which are determined through branching strategies. The basic concept is that during a depth-first search a wrong turn close to the root is first of all very expensive. Second, heuristics work worse the farther away from the solution they are applied. Therefore, decisions close to the root node are likely to fail. Consequently, in a depth-first search the worst decisions are the most expensive ones. The limited discrepancy search solves exactly this problem as it suggests to change rather the decisions made close to the root than the ones the search made later. The improvement compared to a chronological backtrack was shown by experimental results and theoretically proven in \cite{limitedDiscrepancy}.
